Evolution of pre-copulatory and post-copulatory inbreeding behaviour and associated polyandry

### 2016-11-01 ms_pre_post.Rmd
Edit Model: Density regulation subsection

@@

After offspring viability is realised, $\rho$ adult immigrants are added to the focal population. The coefficient of kinship between an immigrant and all other individuals (including native individuals and other immigrants) always equals zero ($k_{ij}=0$). Because kinship coefficient values are calculated directly from the pedigree of the focal population [not from individuals' genomes; see @Duthie], the addition of immigrants introduces non-kin into the population at a constant rate and prevents the mean kinship coefficient of the population from asymptoting to a value of 1 over generations. If the focal population was instead closed ($\rho=0$), then all alleles would quickly be expected to become identical-by-descent among descendants of the ancestral population. To avoid having immigrants affect evolution of tendency for polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory inbreeding strategy ($F_{p}$), immigrants are always male and can therefore be chosen based on their kinship values of zero but not actively affect reproductive decisions through the expression of $P_{p}$, $M_{p}$, or $F_{p}$. To further avoid having immigrants affect evolutionary dynamics, allele values underlying ($P_{a}$), pre-copulatory inbreeding strategy ($M_{a}$), and post-copulatory inbreeding strategy ($F_{a}$) are randomly sampled from normal distributions with means and standard deviations of $P_{a}$, $M_{a}$, and $F_{a}$ values equal to the means and standard deviations of those in the focal population at the time of immigration. Overall, this model of immigration effectively assumes that the focal population receives immigrants from other nearby populations that are subject to the same selection on $P_{p}$, $M_{p}$, and $F_{p}$.

To avoid having unrestricted population growth over generations, we introduce a separate carrying capacity on the total number of females ($K_{f}$) and males ($K_{m}$) in the focal population following immigration [@Guillaume2009; @Duthie]. If at the end of a generation the number of females or males exceeds their respective carrying capacities, then each sex is reduced back to its $K_{f}$ or $K_{m}$ by randomly removing females and males until each sex is at its carrying capacity. Removal of females and males can be interpreted as dispersal outside the focal population, mortality, or as some combination of dispersal and mortality. The remaining females and males within the population form the next generation of adults.

>>>>

After offspring mortality, $\rho$ adult immigrants are added to the focal population. The kinship between an immigrant and all other individuals always equals zero ($k_{ij}=0$). Immigration therefore prevents the mean kinship within the population from asymptoting to one over generations. To ensure that immigrants do not directly affect genotypic or phenotypic values of tendency for polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory inbreeding strategy ($F_{p}$), immigrants are always male. Consequently, they can be chosen as females' mates based on their kinship values of zero but do not actively affect reproductive decisions through the expression of $P_{p}$, $M_{p}$, or $F_{p}$. Further, immigrants $P_{a}$, $M_{a}$, and $F_{a}$ allele values are randomly sampled from normal distributions with means and standard deviations equal to those in the focal population at the time of immigration. We thereby effectively assume that the focal population receives immigrants from other nearby populations that are subject to the same selection on $P_{p}$, $M_{p}$, and $F_{p}$.

To avoid unrestricted population growth, we set separate carrying capacities for the total numbers of females ($K_{f}$) and males ($K_{m}$) in the focal population following immigration [@Guillaume2009; @Duthie]. If at the end of a generation the number of females or males exceeds $K_{f}$ or $K_{m}$  respectively, then individuals are randomly removed until each sex is at its carrying capacity. Such removal can be interpreted as some combination of dispersal and mortality. The remaining females and males form the next generation of potentially breeding adults.

@@
